03 - Analyses coding

### 2022-06-13 scripts/r/03-analyses-coding.Rmd
♻️ - add code to download refitted models from OSF

>>>>

We first download all the refitted models .rds files from the OSF

```{r download-refitted}
cache <- osf_retrieve_node("wds2m")
refitted_rds <- osf_ls_files(cache, "models/refitted", n_max = Inf)

osf_download(
  refitted_rds,
  path = "./data/analyses/models/",
  conflicts = "skip", progress = TRUE, verbose = TRUE
)
```
